$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex
add comma.

To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
we show the variation in fine tuning for $M_X = 20$ TeV, $50$ TeV, $100$
TeV and $10^{16}$ GeV when we scan over the stop masses and mixing,
with $500 \textrm{ GeV} \leq m_{Q_3} , m_{u_3} \leq 10 \textrm{ TeV}$ and
$-3810\textrm{ GeV} \leq A_t \leq -20 \textrm{ GeV}$.  The remaining
parameters we fix such that at $M_{\rm SUSY}$ they have the values
$\mu = -97.5$ GeV, $B = -84.8$ GeV, $M_1 = 92.1$ GeV, $M_2 = 95.9$ GeV,
$M_3 = 352$ GeV, $A_b = -117.9$ GeV, $A_\tau = -7.8$ GeV, $m_{L_i} = 400$ GeV,
$m_{e_i} = 204$ GeV, $m_{Q_{1,2}} = 438$ GeV, $m_{u_{1,2}} = 436$ GeV and
$m_{d_i} = 438$ GeV ($i = 1 , 2 , 3$).  Here we denote by $M_1$, $M_2$ and
$M_3$ the soft gaugino masses for $U(1)$, $SU(2)$ and $SU(3)$, while $A_b$ and
$A_\tau$ are soft trilinear couplings and the $m_\phi$ are soft scalar
masses for the indicated fields.  The soft bilinear coupling $B$ is defined
such that at tree level the mass of the CP-odd MSSM Higgs boson reads
$m_A^2 = 2 B \mu / \sin 2\beta$.  All off-diagonal couplings and scalar masses
are set to zero, as are the first and second generation Yukawa couplings
and soft trilinears.  Although we should stress that making
this choice will lead to a spectrum which is in conflict with the LHC
limits, doing so ensures that fine tuning due to the other parameters
is small, so that we avoid washing out the fine tuning impact of the
stops when the tuning is small\footnote{For models in which the
spectrum is heavier, when the stop masses are small the fine tuning
reaches a lower bound imposed by other heavier parameters.} as can
be the case when the stop masses are less than 1 TeV.  Note that the
Higgs mass is also allowed to vary in this scan, as shown in the right
panel of Fig.~\ref{Fig:mssmstoptuning}.  This illustrates the tuning
problem which people have been worrying about since the discovery of
the 125 GeV Higgs boson as we see that raising the stop masses is also
pushing up the Higgs mass, meaning that heavier Higgs masses require
more fine tuning.  However for a low value of the UV scale this tuning
is not so severe unless the stops are very heavy, and a 125 GeV Higgs
can be obtained without much tuning in this unrealistic case where we
have minimized other sources of tuning.  On the other hand the tuning
becomes more severe as we increase the cutoff such that for $M_X =
10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error even with leading two-loop corrections, which should be considered when interpreting what such results for the miniumum fine tuining in the model, given the discovery of a 125 GeV Higgs.}
for a $125$ GeV Higgs is $\approx 200$, as shown in
Fig.~\ref{Fig:mssmstoptuning}.

>>>>

To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
we show the variation in fine tuning for $M_X = 20$ TeV, $50$ TeV, $100$
TeV and $10^{16}$ GeV when we scan over the stop masses and mixing,
with $500 \textrm{ GeV} \leq m_{Q_3} , m_{u_3} \leq 10 \textrm{ TeV}$ and
$-3810\textrm{ GeV} \leq A_t \leq -20 \textrm{ GeV}$.  The remaining
parameters we fix such that at $M_{\rm SUSY}$ they have the values
$\mu = -97.5$ GeV, $B = -84.8$ GeV, $M_1 = 92.1$ GeV, $M_2 = 95.9$ GeV,
$M_3 = 352$ GeV, $A_b = -117.9$ GeV, $A_\tau = -7.8$ GeV, $m_{L_i} = 400$ GeV,
$m_{e_i} = 204$ GeV, $m_{Q_{1,2}} = 438$ GeV, $m_{u_{1,2}} = 436$ GeV and
$m_{d_i} = 438$ GeV ($i = 1 , 2 , 3$).  Here we denote by $M_1$, $M_2$ and
$M_3$ the soft gaugino masses for $U(1)$, $SU(2)$ and $SU(3)$, while $A_b$ and
$A_\tau$ are soft trilinear couplings and the $m_\phi$ are soft scalar
masses for the indicated fields.  The soft bilinear coupling $B$ is defined
such that at tree level the mass of the CP-odd MSSM Higgs boson reads
$m_A^2 = 2 B \mu / \sin 2\beta$.  All off-diagonal couplings and scalar masses
are set to zero, as are the first and second generation Yukawa couplings
and soft trilinears.  Although we should stress that making
this choice will lead to a spectrum which is in conflict with the LHC
limits, doing so ensures that fine tuning due to the other parameters
is small, so that we avoid washing out the fine tuning impact of the
stops when the tuning is small\footnote{For models in which the
spectrum is heavier, when the stop masses are small the fine tuning
reaches a lower bound imposed by other heavier parameters.} as can
be the case when the stop masses are less than 1 TeV.  Note that the
Higgs mass is also allowed to vary in this scan, as shown in the right
panel of Fig.~\ref{Fig:mssmstoptuning}.  This illustrates the tuning
problem which people have been worrying about since the discovery of
the 125 GeV Higgs boson as we see that raising the stop masses is also
pushing up the Higgs mass, meaning that heavier Higgs masses require
more fine tuning.  However for a low value of the UV scale this tuning
is not so severe unless the stops are very heavy, and a 125 GeV Higgs
can be obtained without much tuning in this unrealistic case where we
have minimized other sources of tuning.  On the other hand the tuning
becomes more severe as we increase the cutoff such that for $M_X =
10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
tuning of $\approx 100 - 1000$ and the minimum tuning we find \footnote{Note that in the calculation of the Higgs mass there is a significant theoretical error, even with leading two-loop corrections, which should be considered when considering what the results imply regarding the miniumum fine tuining in the model consistent with the recent discovery of a 125 GeV Higgs.}
for a $125$ GeV Higgs is $\approx 200$, as shown in
Fig.~\ref{Fig:mssmstoptuning}.
